Seminarium TI 3700\\ Data Analysis on Twitter: An Overview (working title)

### 2014-03-10 authorinstr_2.tex
User modelling + wat andere dingen.

\section{Single tweet analysis}
In this section we will discuss the different types of analysis that can be done on one single tweet. This usually is also the basis for a analysis of a larger amount of tweets or even on a stream of tweets. 
\subsection{Data enrichment}
At the very basis of the analysis of a tweet is data enrichment. Because the length of a tweet is restricted to 140 characters, the users of Twitter use language in creative ways. This way of communicating makes it sometimes, even for humans, hard to understand what a tweet is about. To get a better understanding of the meaning of a tweet, a context is needed. For humans this is done by linking the concepts from the tweet to earlier acquired knowledge. The same thing can be done by computers. Two stages can be defined in this process, first the extraction of the concepts from the tweet, after that a context can be created by linking the tweet to other sources.
\subsubsection{Concept extraction}
In this case by concepts we mean named entities such as names of locations, people and organizations. To recognize these entities multiple learning algorithms or even combinations of learning algorithms have been proposed. The most common is statistical learning. Think of algorithms like Maximum Entropy Models, Hidden Markov Models or neural networks. Other proposed algorithms are AdaBoost.MH, employed memory-based learning, transformation-based learning, support vector machines and conditional random fields. All of them in decreasing frequency of use.\cite{EntityRecognition} Florian et al. have shown that combining multiple classifiers can increase the performance, compared to the best performing classifier, by 17-21 \%.\cite{ClassifierCombination} After the entities have been found, labels are assigned to distinguish between a person, an organization or location. Then Abel et al. propose to use the RDF.\cite{AdaptiveSearch} By doing so sources from the Semantic Web (e.g. DBpedia \footnote{http://dbpedia.org/}) can now be leveraged to enrich the data. Another advantage of using RDF is that RDF is a Semantic Web standard recommended by the W3C\footnote{http://www.w3.org/RDF/}. Because W3C recommends to use this model, most likely a lot of other sources also use this model. This will give a much bigger knowledge base to enrich the data from.
\subsubsection{Context creation}
The problem of linking tweets to another source of information poses the biggest issue in data enrichment. The tweets themselves do not provide much information. Fortunately, Kwak et al. have shown that the topic of over 85\% of the of the tweets is related to news \cite{newsmedia}. This knowledge can be leveraged to create a context for most of the tweets.  This is what Abel et al. proposed to do\cite{enrichmentForProfiling}. They linked tweets to mainstream news networks like CNN, BBC and New York Times.

@@

\subsubsection{Emoticons}
Other than semantical analysis we can also use other data from tweets. A good sentiment indicator are emoticons. Twitter users use emoticons (e.g. ":-)", ":(" or "=(") to indicate their mood.\cite{twitterSentiment} Since the number of emoticons is limited a sentiment can easily be assigned manually. The information from the emoticons can be leveraged in two ways
\begin{enumerate}
\item \textbf{Labeling:} The emoticons can be used to assign a sentiment to a tweet. This can be a very useful asset to take into account when assigning a sentiment to a tweet. The emoticons can be considered unigrams feature for some classifier. There they will be strong evidence for a certain sentiment.
\item \textbf{Training:} Because of their clear evidence for a sentiment emoticons can also be used to build a training corpus for a supervised learning algorithm. Twitter can be queried for "positive" emoticons and "negative" emoticons and then, by assuming the emoticon reflects the sentiment of message, the tweet can be labeled accordingly.\cite{moodLens} 
\end{enumerate}
We now see that emoticons can be used to extract a sentiment from a tweet. However, they are not sufficient to just use emoticons to label the tweets. Simply because not all tweets contain emoticons.
\subsubsection{Usage}
The possibilities of sentiment analysis are not too hard to imagine. Every company wants to know how their newly launched product is doing, film makes want to know what people think about their new movie and politicians want to know how they are doing for the next elections. Using sentiment analysis all this information will become available\cite{machineLearning}. 
\subsection{Metadata analysis (opt)}

\section{Tweet stream analysis}
\subsection{Statistics}
\subsection{User Modelling}
\subsection{User Classification}
User classification is the problem of classification of users based on (1) their metadata such as age, location and job and (2) the tweets a user has posted. In this chapter we will discuss some features used to classify users and some use-cases.

@@

To classify the users a one vs all classifier is trained. (Which will recorgnize one party vs all other parties. 
\subsection{Tag based analysis}

>>>>

\section{Single tweet analysis}
In this section we will discuss the different types of analysis that can be done on one single tweet. This usually is also the basis for a analysis of a larger amount of tweets or even on a stream of tweets. 
\subsection{Data enrichment}
At the very basis of the analysis of a tweet is data enrichment. Because the length of a tweet is restricted to 140 characters the users of Twitter use language in creative ways that sometimes make it, even for humans, hard to understand what a tweet is about. To get a better understanding of the meaning of a tweet, a context is needed. For humans this is done by linking the information from the tweet to earlier acquired knowledge. The same thing can be done by computers. 
\subsubsection{Context creation}
The problem of linking tweets to another source of information poses the biggest issue in data enrichment. The tweets themselves do not provide much information. Fortunately, Kwak et al. have shown that the topic of over 85\% of the of the tweets is related to news \cite{newsmedia}. This knowledge can be leveraged to create a context for most of the tweets.  This is what Abel et al. proposed to do\cite{enrichmentForProfiling}. They linked tweets to mainstream news networks like CNN, BBC and New York Times.

@@

\subsubsection{Emoticons}
Other than semantical analysis we can also use other data from tweets. A good sentiment indicator are emoticons. Twitter users use emoticons (e.g. ":-)", ":(" or "=(") to indicate their mood.\cite{twitterSentiment} Since the number of emoticons is limited a sentiment can easily be assigned manually. The information from the emoticons can be leveraged in two ways
\begin{enumerate}
\item \textbf{Labeling:} The emoticons can be used to assign a sentiment to a tweet. This can be a very useful asset to take into account when assigning a sentiment to a tweet. The emoticons can be considered unigrams feature for some classifier. There they will be strong evidence for a certain sentiment.
\item \textbf{Training:} Because of their clear evidence for a sentiment emoticons can also be used to build a training corpus for a supervised learning algorithm. Twitter can be queried for "positive" emoticons and "negative" emoticons and then, by assuming the emoticon reflects the sentiment of message, the tweet can be labeled accordingly.\cite{moodLens} 
\end{enumerate}
We now see that emoticons can be used to extract a sentiment from a tweet. However, they are not sufficient to just use emoticons to label the tweets. Simply because not all tweets contain emoticons.
\subsubsection{Usage}
The possibilities of sentiment analysis are not too hard to imagine. Every company wants to know how their newly launched product is doing, film makes want to know what people think about their new movie and politicians want to know how they are doing for the next elections. Using sentiment analysis all this information will become available\cite{machineLearning}. 
\subsection{Concept extraction}
\subsection{Metadata analysis (opt)}

\section{Tweet stream analysis}
\subsection{Statistics}

\subsection{User Classification}
User classification is the problem of classification of users based on (1) their metadata such as age, location and job and (2) the tweets a user has posted. In this chapter we will discuss User Models, some features used to classify users and some use-cases. 
\subsubsection{User Models}
Before it is possible to classify a user, it is useful to create a model of a user. In their paper Fabel et al compare the following three ways to model a user. \cite{usermodel}
\begin{itemize}
\item Hashtag-based
\item Entity-based
\item Topic-based

\end{itemize}
After all these approaches are used on the same dataset it appears that the variety of entity-based profiles was much higher than the hashtag based approach. \cite{usermodel} Furthermore the hashtag-based approach fails to create a profile for 5.5\% of the users where the other approaches don't have this problem.

@@

To classify the users a one vs all classifier is trained. (Which will recorgnize one party vs all other parties.) After this all information is combined to predict a political party for each user. 
\subsection{Tag based analysis}
